Paper_analyses

### 2021-09-07 Figures.Rmd
a few new updates
- plots, checks

@@

colnames(clustering_agg_JASPtest)
clustering_agg_JASPtest<- subset(clustering_agg_JASPtest, !is.na(clustering_agg_JASPtest$clusters))
pca_res <- prcomp(clustering_agg_JASPtest[,c(24,23,19)], center = TRUE, scale. = FALSE)
plot_data <- cbind(as.data.frame(pca_res$x[, 1:2]), labels = clustering_agg_JASPtest$clusters)
plot_data$labels<- factor(plot_data$labels)
# stat_el
# plot_data$
plots_paper$PCA_clust

plot_data%>%
  subset(!is.na(labels))%>%
   # subset(!is.na(cluster))%>%
  ggplot( aes(x = PC1, y = PC2, colour = labels)) +
  geom_point(size = 1, alpha = .8)+
  # geom_text(aes(label= test$stimDescription), alpha = .7, size = 5)+
  # stat_ellipse()+
  # stat_ellipse(aes(x = PC1,y=PC2,
  #                  lty=labels,
  #                  fill=labels, 
  #                  color=labels),
  #   geom="polygon",
  #   alpha=0.2, 
  #   size = 1.5)+
  # scale_fill_manual(values=c("red","green","blue"))+
    # scale_color_manual(values=c("red","green","blue"))+
  # scale_linetype_manual(values=c(1,2,3))+
  ylab("Componet 2")+
  xlab("Component 1")+
  p$graphstyle +

@@

unique(tmp.df4_full_stim_downs_jun2021_60bins_no_na1$ssid)
clustering_new %>%
  subset(!is.na(Cluster))%>%
  # subset(ssid_num>303)%>%^
  group_by(ssid, Cluster)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # mutate(arousal2 = abs(arousal))%>%
  subset(arousal> -9)%>%
  ggboxplot(x = "Cluster", y = "arousal",
          color = "Cluster")+
  geom_jitter(width = .1, alpha = .2)+
    stat_summary(aes(group =ssid), geom =  'line', alpha = .2, size = .1)+
  xlab("Cluster")+
  ylab("Subjective arousal \n (calm - agitated)")+
  p$graphstyle+ theme(legend.position = "none")
  # stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  # stat_compare_means(label.y = 9)
plots_paper$arousal_clust
# valence cluster

plots_paper$valence_clust<- tmp.df4_full_stim_downs_jun2021_60bins_no_na %>%
  group_by(ssid, Cluster)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  mutate(arousal2 = abs(arousal))%>%
  subset(arousal> -9)%>%
  ggboxplot(x = "Cluster", y = "valence",
          color = "Cluster")+
  geom_jitter(width = .1, alpha = .2)+
    stat_summary(aes(group =ssid), geom =  'line', alpha = .2, size = .1)+
  xlab("Cluster")+
  ylab("Subjective valence \n (negative - positive)")+
  p$graphstyle+ theme(legend.position = "none")
  # stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  # stat_compare_means(label.y = 9)

@@

>>>>

https://uc-r.github.io/kmeans_clustering

@@

colnames(clustering_agg_JASPtest)
clustering_agg_JASPtest<- subset(clustering_agg_JASPtest, !is.na(clustering_agg_JASPtest$clusters))
pca_res <- prcomp(clustering_agg_JASPtest[,c(24,23,19)], center = TRUE, scale. = TRUE)
plot_data <- cbind(as.data.frame(pca_res$x[, 1:2]), labels = clustering_agg_JASPtest$clusters)
plot_data$labels<- factor(plot_data$labels)
# stat_el
# plot_data$
plots_paper$PCA_clust

plot_data%>%
  subset(!is.na(labels))%>%
   # subset(!is.na(cluster))%>%
  ggplot( aes(x = PC1, y = PC2, colour = labels)) +
  geom_point(size = 1, alpha = .8)+
  # geom_text(aes(label= test$stimDescription), alpha = .7, size = 5)+
  stat_ellipse()+
  # stat_ellipse(aes(x = PC1,y=PC2,
  #                  lty=labels,
  #                  fill=labels,
  #                  color=labels),
  #   geom="polygon",
  #   alpha=0.2,
  #   size = 1.5)+
  # scale_fill_manual(values=c("red","green","blue"))+
    # scale_color_manual(values=c("red","green","blue"))+
  # scale_linetype_manual(values=c(1,2,3))+
  ylab("Componet 2")+
  xlab("Component 1")+
  p$graphstyle +

@@

unique(tmp.df4_full_stim_downs_jun2021_60bins_no_na1$ssid)
plots_paper$arousal_clust<- clustering_new %>%
  subset(!is.na(Cluster))%>%
  # subset(ssid_num>303)%>%^
  group_by(ssid, Cluster)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # mutate(arousal2 = abs(arousal))%>%
  subset(arousal> -9)%>%
  ggboxplot(x = "Cluster", y = "arousal",
          color = "Cluster")+
  geom_jitter(width = .1, alpha = .2)+
    stat_summary(aes(group =ssid), geom =  'line', alpha = .2, size = .1)+
  xlab("Cluster")+
  ylab("Subjective arousal \n (calm - agitated)")+
  p$graphstyle+ theme(legend.position = "none")
  # stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  # stat_compare_means(label.y = 9)
plots_paper$arousal_clust
# valence cluster

plots_paper$valence_clust<- clustering_new %>%
  subset(!is.na(Cluster))%>%
  group_by(ssid, Cluster)%>%

  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  mutate(arousal2 = abs(arousal))%>%
  subset(arousal> -9)%>%
  ggboxplot(x = "Cluster", y = "valence",
          color = "Cluster")+
  geom_jitter(width = .1, alpha = .2)+
    stat_summary(aes(group =ssid), geom =  'line', alpha = .2, size = .1)+
  xlab("Cluster")+
  ylab("Subjective valence \n (negative - positive)")+
  p$graphstyle+ theme(legend.position = "none")
  # stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  # stat_compare_means(label.y = 9)

@@

```{r}
tsne::tsne()

Phasic responses reveal limited cross correlations across physiological signals
```{r}

correlation_plot<- db_full6new_hr_fix_stim_nt1.1 %>%
  mutate(log_BIO_CDA.PhasicMax = log1p(BIO_CDA.PhasicMax+.1))%>%
  subset(ssid!= "347")%>%
  subset(!is.na(mediansplit_ground_valence))%>%
  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
  group_by(ssid)%>%
  mutate(Bio_Mean_HR_dif = scale(Bio_Mean_HR_dif, center = TRUE, scale = TRUE)[,1],
         pup_basCor = scale(pup_basCor, center = TRUE, scale = TRUE)[,1],
         log_BIO_CDA.PhasicMax = scale(log_BIO_CDA.PhasicMax, center = TRUE, scale = TRUE)[,1])%>%
  group_by(ssid, mediansplit_ground_valence)%>%
  mutate(cor_hr_pup = cor(Bio_Mean_HR_dif, pup_basCor, use = "complete"))%>%
  mutate(cor_hr_scr = cor(Bio_Mean_HR_dif, log_BIO_CDA.PhasicMax, use = "complete"))%>%
  mutate(cor_pup_scr = cor(pup_basCor, log_BIO_CDA.PhasicMax, use = "complete"))%>%
  select(c(ssid, mediansplit_ground_valence,cor_hr_pup, cor_hr_scr, cor_pup_scr))%>%
  gather(key, value, -ssid,-mediansplit_ground_valence)%>%
  group_by(ssid,mediansplit_ground_valence, key, value)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(key, value, color = key))+
  geom_hline(yintercept = 0, size = 1.5, linetype = "dashed", alpha = .5)+
  geom_line(aes(group = ssid), se = F, color = "black", alpha = .2)+
  geom_jitter(width = .1, alpha = .5)+

  stat_summary(geom = 'pointrange', color = "black")+
    facet_grid(~mediansplit_ground_valence)+

  p$graphstyle+
  ylab("Correlation")+
  scale_x_discrete(
        labels=c("HR vs. Pupil", "HR vs. SCR", "Pupil vs. SCR"))+
  theme(axis.title.x = element_blank(), axis.text.x = element_text( 
                           size=14, angle=45), legend.position = "none")+
  scale_color_brewer(palette = "Dark2")
  # ggpubr::ggviolin(aes(x = "key", y = "value"))

  # subset(db_full6new_hr_fix_stim_nt1.1, Bio_Mean_HR_dif )

  correlation_plot

  db_full6new_hr_fix_stim_nt1.1

  ?cut
  db_full6new_hr_fix_stim_nt1.1$valeence_groun_3cat<- cut(db_full6new_hr_fix_stim_nt1.1$ValenceMean, breaks = 3, labels = c("negative", "mid", "positive"))

  db_full6new_hr_fix_stim_nt1.1 %>%
  mutate(log_BIO_CDA.PhasicMax = log1p(BIO_CDA.PhasicMax+.1))%>%
  subset(ssid!= "347")%>%
  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
    subset(!is.na(valeence_groun_3cat))%>%
  group_by(ssid)%>%
  mutate(Bio_Mean_HR_dif = scale(Bio_Mean_HR_dif, center = TRUE, scale = TRUE)[,1],
         pup_basCor = scale(pup_basCor, center = TRUE, scale = TRUE)[,1],
         log_BIO_CDA.PhasicMax = scale(log_BIO_CDA.PhasicMax, center = TRUE, scale = TRUE)[,1])%>%
    group_by(ssid, valeence_groun_3cat)%>%
  mutate(cor_hr_pup = cor(Bio_Mean_HR_dif, pup_basCor, use = "complete"))%>%
  mutate(cor_hr_scr = cor(Bio_Mean_HR_dif, log_BIO_CDA.PhasicMax, use = "complete"))%>%
  mutate(cor_pup_scr = cor(pup_basCor, log_BIO_CDA.PhasicMax, use = "complete"))%>%
  select(c(ssid,valeence_groun_3cat, cor_hr_pup, cor_hr_scr, cor_pup_scr))%>%
  gather(key, value, -ssid, - valeence_groun_3cat)%>%
  group_by(ssid, key, value, valeence_groun_3cat)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(valeence_groun_3cat, value, color = valeence_groun_3cat))+
  geom_hline(yintercept = 0, size = 1.5, linetype = "dashed", alpha = .5)+
    geom_hline(yintercept = .2, size = 1.5, linetype = "dashed", alpha = .5)+
    geom_hline(yintercept = -.2, size = 1.5, linetype = "dashed", alpha = .5)+
  geom_line(aes(group = ssid), se = F, color = "black", alpha = .2)+
  geom_jitter(width = .1, alpha = .5)+

  stat_summary(geom = 'pointrange', color = "black")+
    facet_grid(~key)+

  p$graphstyle+
  ylab("Correlation")+
  scale_x_discrete(
        labels=c("HR vs. Pupil", "HR vs. SCR", "Pupil vs. SCR"))+
  theme(axis.title.x = element_blank(), axis.text.x = element_text( 
                           size=14, angle=45))+
  scale_color_brewer(palette = "Dark2")

```{r}
ggsav

 hr_rmmcorr<- db_full6new_hr_fix_stim_nt1.1 %>%
  # mutate(log_BIO_CDA.PhasicMax = log1p(BIO_CDA.PhasicMax+.1))%>%
  subset(ssid!= "347")%>%
  subset(Bio_Mean_HR_dif_outl!= "outlier")
plot(rmcorr::rmcorr(participant = "ssid", measure1 = "Bio_Mean_HR_dif", measure2 = "pup_basCor", data = hr_rmmcorr))

plot(rmcorr::rmcorr(participant = "ssid", measure1 = "log_BIO_CDA.PhasicMax_z", measure2 = "pup_basCor", data = hr_rmmcorr))

hr_rmmcorr<- hr_rmmcorr%>%
  group_by(ssid)%>%
  mutate(log_BIO_CDA.PhasicMax_z= scale(log_BIO_CDA.PhasicMax, center =TRUE, scale = TRUE))

plot(rmcorr::rmcorr(participant = "ssid", measure1 = "log_BIO_CDA.PhasicMax_z", measure2 = "Bio_Mean_HR_dif", data = hr_rmmcorr))

correlation_plot

scater_pupil_HR<- db_full6new_hr_fix_stim_nt1.1 %>%
  subset(!is.na(stimDescription))%>%
  subset(!is.na(mediansplit_ground_valence))%>%
  group_by(stimIAPS,mediansplit_ground_valence, stimDescription)%>%
  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(Bio_Mean_HR_dif, pup_basCor))+
  geom_point(aes(color = mediansplit_ground_valence), size = 2, alpha = .6)+
  geom_text(aes(label = stimDescription,olor = mediansplit_ground_valence), alpha = .3)+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()+
  xlab(expression("Average "*Delta*" heart rate (bpm)"))+
  # xlab("Average heart rate difference")+
  ylab("Average pupil change (au)")+
  p$graphstyle

scater_pupil_HR

db_full6new_hr_fix_stim_nt1.1 %>%
  subset(!is.na(stimDescription))%>%
  subset(!is.na(mediansplit_ground_valence))%>%
  group_by(stimIAPS, stimDescription,mediansplit_ground_valence)%>%
  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(Bio_Mean_HR_dif, pup_basCor, color = mediansplit_ground_valence))+
  geom_point(size = 2, alpha = .6)+
  geom_text(aes(label = stimDescription), alpha = .3)+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()+
  xlab(expression("Average "*Delta*" heart rate (bpm)"))+
  # facet_grid(~mediansplit_ground_valence)+
  # xlab("Average heart rate difference")+
  ylab("Average pupil change (au)")+
  p$graphstyle

db_full6new_hr_fix_stim_nt1.1$log_BIO_CDA.PhasicMax_z<- scale(db_full6new_hr_fix_stim_nt1.1$log_BIO_CDA.PhasicMax, center =  TRUE,scale = TRUE)[,1]

db_full6new_hr_fix_stim_nt1.1 %>%
  subset(!is.na(stimDescription))%>%
  subset(!is.na(mediansplit_ground_valence))%>%
  group_by(stimIAPS, stimDescription,mediansplit_ground_valence)%>%
  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(Bio_Mean_HR_dif, log_BIO_CDA.PhasicMax_z, color = mediansplit_ground_valence))+
  geom_point(size = 2, alpha = .6)+
  geom_text(aes(label = stimDescription), alpha = .3)+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()+
  xlab(expression("Average "*Delta*" heart rate (bpm)"))+
  # facet_grid(~mediansplit_ground_valence)+
  # xlab("Average heart rate difference")+
  ylab("Average pupil change (au)")+
  p$graphstyle

db_full6new_hr_fix_stim_nt1.1$stimIAPS2<- as.factor(substr(db_full6new_hr_fix_stim_nt1.1$stimIAPS, 1,4))

macthed_test$matched<- "matched"

macthed_test$stimIAPS2<- as.factor(macthed_test$stimIAPS2)

# mac
testmatched_hr_stim<- left_join(macthed_test,db_full6new_hr_fix_stim_nt1.1,  by = c("stimIAPS2"))

testmatched_hr_stim %>%
  subset(!is.na(mediansplit_ground_valence))%>%
  subset(!is.na(matched))%>%
  group_by(stimIAPS, stimDescription,mediansplit_ground_valence)%>%
  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ungroup()%>%
  mutate(log_BIO_CDA.PhasicMax_z = scale(log_BIO_CDA.PhasicMax), pup_basCor_z = scale(pup_basCor))%>%
  ggplot(aes(Bio_Mean_HR_dif, pup_basCor, color = mediansplit_ground_valence))+
  geom_point(size = 2, alpha = .6)+
  geom_text(aes(label = stimDescription), alpha = .3)+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()+
  xlab(expression("Average "*Delta*" heart rate (bpm)"))+
  # facet_grid(~mediansplit_ground_valence)+
  # xlab("Average heart rate difference")+
  ylab("Average pupil change (au)")+
  p$graphstyle

testmatched_hr_stim %>%
  subset(!is.na(mediansplit_ground_valence))%>%
  subset(!is.na(matched))%>%
  group_by(stimIAPS, stimDescription,mediansplit_ground_valence)%>%
  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ungroup()%>%
  mutate(log_BIO_CDA.PhasicMax_z = scale(log_BIO_CDA.PhasicMax), pup_basCor_z = scale(pup_basCor))%>%
  ggplot(aes(Bio_Mean_HR_dif, log_BIO_CDA.PhasicMax_z, color = mediansplit_ground_valence))+
  geom_point(size = 2, alpha = .6)+
  geom_text(aes(label = stimDescription), alpha = .3)+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()+
  xlab(expression("Average "*Delta*" heart rate (bpm)"))+
  # facet_grid(~mediansplit_ground_valence)+
  # xlab("Average heart rate difference")+
  ylab("Average pupil change (au)")+
  p$graphstyle

testmatched_hr_stim %>%
  subset(!is.na(mediansplit_ground_valence))%>%
  subset(!is.na(matched))%>%
  group_by(stimIAPS, stimDescription,mediansplit_ground_valence)%>%
  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ungroup()%>%
  mutate(log_BIO_CDA.PhasicMax_z = scale(log_BIO_CDA.PhasicMax), pup_basCor_z = scale(pup_basCor))%>%
  ggplot(aes(pup_basCor_z, log_BIO_CDA.PhasicMax_z, color = mediansplit_ground_valence))+
  geom_point(size = 2, alpha = .6)+
  geom_text(aes(label = stimDescription), alpha = .3)+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()+
  xlab(expression("Average "*Delta*" heart rate (bpm)"))+
  # facet_grid(~mediansplit_ground_valence)+
  # xlab("Average heart rate difference")+
  ylab("Average pupil change (au)")+
  p$graphstyle

library(patchwork)
patch_correlations <- correlation_plot+scater_pupil_HR+
   plot_layout(ncol = 2)+plot_annotation(tag_levels = "A")
patch_correlations
ggsave("patch_correlations.tiff", patch_correlations, device = "tiff", width = 12, height = 5, dpi = 800)
```

### 2021-09-07 Paper_Analyses_subj_obje_arousal.Rmd
a few new updates
- plots, checks

# pollu
db_full4new_stim_screen_pupil_nopract$valence_c_sq<- db_full4new_stim_screen_pupil_nopract$valence**2
polyyrelation<- lmer(arousal_c ~ valence_c+valence_c_sq+ (1|ssid) + (1|stimIAPS),
                     REML = FALSE,
                     data = db_full4new_stim_screen_pupil_nopract)
```

@@

nrow(db_full4new_stim_screen_pupil_nopract_nt_304)
nrow(testmatched_scr)
testmatched_scr<- left_join(macthed_test, db_full4new_stim_screen_pupil_nopract_nt_304, by = "stimIAPS2")

@@

inter_bio1<- lmer(Bio_Mean_HR_dif~ pup_basCor +BIO_CDA.PhasicMax_z + (1|ssid)+ (1|stimIAPS), 
                 REML = FALSE,
                 data = db_full6new_hr_fix_stim_nt1.1)

summary(inter_bio1)

inter_bio2<- lmer(log1p(BIO_CDA.PhasicMax+.1)~ Bio_Mean_HR_dif + pup_basCor + (1|ssid)+ 
                    (1|stimIAPS), 
                 REML = FALSE,
                 data = db_full6new_hr_fix_stim_nt1.1)

summary(inter_bio2)

@@

db_full6new_hr_fix_stim_nt1.1 %>%
  mutate(log_BIO_CDA.PhasicMax = log1p(BIO_CDA.PhasicMax+.1))%>%
  subset(ssid!= "347")%>%
  group_by(ssid)%>%
  mutate(Bio_Mean_HR_dif = scale(Bio_Mean_HR_dif, center = TRUE, scale = TRUE)[,1],
         pup_basCor = scale(pup_basCor, center = TRUE, scale = TRUE)[,1],
         log_BIO_CDA.PhasicMax = scale(log_BIO_CDA.PhasicMax, center = TRUE, scale = TRUE)[,1])%>%
  mutate(cor_hr_pup = cor(Bio_Mean_HR_dif, pup_basCor, use = "complete"))%>%
  mutate(cor_hr_scr = cor(Bio_Mean_HR_dif, log_BIO_CDA.PhasicMax, use = "complete"))%>%
  mutate(cor_pup_scr = cor(pup_basCor, log_BIO_CDA.PhasicMax, use = "complete"))%>%
  select(c(ssid, cor_hr_pup, cor_hr_scr, cor_pup_scr))%>%
  gather(key, value, -ssid)%>%
  group_by(ssid, key, value)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(key, value))+
  geom_jitter(width = .1, alpha = .1)+
  geom_line(aes(group = ssid), se = F)+
  stat_summary(geom = 'pointrange')

>>>>

# pollu
db_full4new_stim_screen_pupil_nopract$valence_c_sq<- db_full4new_stim_screen_pupil_nopract$valence**2
polyyrelation <- lmer(arousal_c ~ valence_c+valence_c_sq+ (1|ssid) + (1|stimIAPS),
                     REML = FALSE,
                     data = db_full4new_stim_screen_pupil_nopract)

summary(polyyrelation)

polyyrelation1 <- lmer(arousal_c ~ valence_c + (1|ssid) + (1|stimIAPS),
                     REML = FALSE,
                     data = db_full4new_stim_screen_pupil_nopract)

polyyrelation3 <- lmer(arousal_c ~ valence_c_sq+ (1|ssid) + (1|stimIAPS),
                     REML = FALSE,
                     data = subset(db_full4new_stim_screen_pupil_nopract, )

summary(polyyrelation)
summary(polyyrelation)

MuMIn::r.squaredGLMM(polyyrelation)
MuMIn::r.squaredGLMM(polyyrelation1)
MuMIn::r.squaredGLMM(polyyrelation3)

anova(polyyrelation3, polyyrelation, polyyrelation1)

db_full4new_stim_screen_pupil_nopract%>%
  subset(Group == "NT")%>%
  mutate(ssid= as.numeric(ssid))%>%
  subset(ssid = 20)%>%
  ggplot(aes(valence_c, arousal_c, color = ssid))+
  geom_point()+
  stat_ellipse()+
  stat_smooth()

@@

nrow(db_full4new_stim_screen_pupil_nopract_nt_304)
nrow(testmatched_scr)
testmatched_scr<- right_join(macthed_test, db_full4new_stim_screen_pupil_nopract_nt_304, by = "stimIAPS2")

@@

inter_bio1<- lmer(Bio_Mean_HR_dif~ pup_basCor +BIO_CDA.PhasicMax_z + (1|ssid)+ (1|stimIAPS), 
                 REML = FALSE,
                 data = subset(db_full6new_hr_fix_stim_nt1.1, Bio_Mean_HR_dif_outl!= "outlier"))

summary(inter_bio1)
# MuMin::

inter_bio2<- lmer(log1p(BIO_CDA.PhasicMax+.1)~ Bio_Mean_HR_dif + pup_basCor + (1|ssid)+ 
                    (1|stimIAPS), 
                 REML = FALSE,
                 data = subset(db_full6new_hr_fix_stim_nt1.1, Bio_Mean_HR_dif_outl!= "outlier"))

db_full6new_hr_fix_stim_nt1.1$log_BIO_CDA.PhasicMax<- log1p(db_full6new_hr_fix_stim_nt1.1$BIO_CDA.PhasicMax+.1)
summary(inter_bio2)

@@

db_full6new_hr_fix_stim_nt1.1 %>%
  mutate(log_BIO_CDA.PhasicMax = log1p(BIO_CDA.PhasicMax+.1))%>%
  subset(ssid!= "347")%>%
  group_by(ssid)%>%
  mutate(Bio_Mean_HR_dif = scale(Bio_Mean_HR_dif, center = TRUE, scale = TRUE)[,1],
         pup_basCor = scale(pup_basCor, center = TRUE, scale = TRUE)[,1],
         log_BIO_CDA.PhasicMax = scale(log_BIO_CDA.PhasicMax, center = TRUE, scale = TRUE)[,1])%>%
  mutate(cor_hr_pup = cor(Bio_Mean_HR_dif, pup_basCor, use = "complete"))%>%
  mutate(cor_hr_scr = cor(Bio_Mean_HR_dif, log_BIO_CDA.PhasicMax, use = "complete"))%>%
  mutate(cor_pup_scr = cor(pup_basCor, log_BIO_CDA.PhasicMax, use = "complete"))%>%
  select(c(ssid, cor_hr_pup, cor_hr_scr, cor_pup_scr))%>%
  gather(key, value, -ssid)%>%
  group_by(ssid, key, value)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(key, value))+
  geom_jitter(width = .1, alpha = .1)+
  geom_line(aes(group = ssid), se = F)+
  stat_summary(geom = 'pointrange')+
  geom_hline(yintercept = 0, size = 1.5, linetype = "dashed")+
  p$graphstyle

db_full6new_hr_fix_stim_nt1.1 %>%
  mutate(log_BIO_CDA.PhasicMax = log1p(BIO_CDA.PhasicMax+.1))%>%
  subset(!is.na(stimIAPS))%>%
  group_by(stimIAPS)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ungroup()%>%
  # group_by(stimIAPS)%>%
  mutate(cor_hr_pup = cor(Bio_Mean_HR_dif, pup_basCor, use = "complete"))%>%
  mutate(cor_hr_scr = cor(Bio_Mean_HR_dif, log_BIO_CDA.PhasicMax, use = "complete"))%>%
  mutate(cor_pup_scr = cor(pup_basCor, log_BIO_CDA.PhasicMax, use = "complete"))%>%
  select(c(stimIAPS, cor_hr_pup, cor_hr_scr, cor_pup_scr))%>%
  gather(key, value, -stimIAPS)%>%
  group_by(stimIAPS, key, value)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(key, value))+
  geom_hline(yintercept = 0, size = 1.5, linetype = "dashed")+
  geom_jitter(width = .1, alpha = .1)+
  geom_line(aes(group = stimIAPS), se = F)+
  stat_summary(geom = 'pointrange')+
  # ggpubr::stat_compare_means(paired = FALSE)+
  p$graphstyle

db_full6new_hr_fix_stim_nt1.1 %>%
  group_by(ssid)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(Bio_Mean_HR_dif, pup_basCor))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

db_full6new_hr_fix_stim_nt1.1 %>%
  group_by(ssid)%>%
  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(Bio_Mean_HR_dif, pup_basCor))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

db_full6new_hr_fix_stim_nt1.1 %>%
  group_by(stimIAPS)%>%
  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(Bio_Mean_HR_dif, pup_basCor))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()
